\titel

### 2014-03-10 presentation-plan/Plan_presentation_monday.tex
Answer Luis' questions

STRIPS is considered one of the first planning algorithms and
representations.~\cite{lavalle2006planning}. It is a very simple logic based
only on literal. It's very nice to describe planning problems in a
descriptive way that closely corresponds to the application. Also due to the
operator definition (action/preconditions) it's possible to describe complex

@@

\subsubsection{Questions posted on blackboard}
\begin{itemize}
\item When aggregating RFF does not update the current partial policy. How does this algorithm handles in dynamic environments, whereas the current partial policy might be no longer valid?

\item RFF receives a tuple MDP planning problem (M, s0, G, p), where the states are already defined in M, which means that the environment is known.
Is RFF applicable in unknown environments? If not, is it possible to adjust it so that it becomes applicable?
\end{itemize}

@@

>>>>

STRIPS is considered one of the first planning algorithms and
representations.~\cite{lavalle2006planning}. It is a very simple logic based
only on literal. It's very nice to describe planning problems in a
descriptive way that closely corresponds to the application. Also due to the
operator definition (action/preconditions) it's possible to describe complex
systems. After STRIPS many STRIPS-inspired have been in introduced.

@@

\subsubsection{Questions posted on blackboard}

\begin{itemize}
	\item \textbf{Q}: When aggregating RFF does not update the current partial
		policy. How does this algorithm handles in dynamic environments,
		whereas the current partial policy might be no longer valid? \\
		\textbf{A}: RFF assumes a MDP, where everything is known. RFF generates
		a policy off-line, but if that policy is used in an environment that
		does not equal to the MDP/world it started with it will fail.

	\item \textbf{Q}: RFF receives a tuple MDP planning problem $(M, s0, G,
		\rho)$, where the states are already defined in M, which means that
		the environment is known.  Is RFF applicable in unknown environments?
		If not, is it possible to adjust it so that it becomes applicable? \\
		\textbf{A}: RFF works only for MDPs. In an MDP it is assumed that it
		is fully observable. In cases you describe, it is not, which people
		invented POMDPs for. POMDPs have different algorithms, for example in
		the paper about POMDPs which translates a POMDP to a classical planning
		problem.

@@

	\begin{itemize}
		\item \emph{``Probabilistic Planning via Determinization in Hindsight''} (2008) \\
			Improves FF-Replan with hindsight optimization.
		\item \emph{``Fast Incremental Policy Compilation from Plans in Hybrid Probabilistic Domains''}
			\begin{itemize}
				\item Extends from discrete states to continues
				\item Like \texttt{RFF} but additional heuristics and usage of \texttt{Metric-FF}
			\end{itemize}
		\item \emph{``Planning under partial observability by classical replanning: Theory and experiments''} (2011) \\
			Translates a POMDP to a classical planning problem where it can use \texttt{FF}.
	\end{itemize}

### 2014-03-10 presentation/presa.tex
Fixing indentation
Add RFF problem description
Answer Luis' questions

\emph{ insert image how hash table is filled}

@@

  \begin{itemize}
    \item Shortcomings
	\begin{itemize}
        	\item Probabilistic effects are treated as equal

\includegraphics[scale=0.5]{images/blindfold.jpg}

	\end{itemize}
   \item Means of improvement
   \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Shortcomings
	\begin{itemize}
        	\item Probabilistic effects are treated as equal
	\item Only works well if the outcomes are likely
\includegraphics[scale=0.5]{images/direction-road-maze.jpg}
	\end{itemize}
   \item Means of improvement

@@

  \begin{itemize}
    \item Problem
      \begin{itemize}
        \item MDPs can be computationally intensive
        \item MDPs typically enumerate the entire state and action space
      \end{itemize}
    \item Motivation
      \begin{itemize}
        \item FF-Replan showed MDP determinization and replanning techniques
        \item However, it stops after the first computed path to a goal
        \item May generate same path over and over
        \item Does not generate a policy
      \end{itemize}
  \end{itemize}

@@

>>>>

      \emph{insert image how hash table is filled}

@@

  \begin{itemize}
    \item Shortcomings
      \begin{itemize}
        \item Probabilistic effects are treated as equal
          \includegraphics[scale=0.5]{images/blindfold.jpg}
      \end{itemize}
    \item Means of improvement
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Shortcomings
      \begin{itemize}
        \item Probabilistic effects are treated as equal
        \item Only works well if the outcomes are likely
          \includegraphics[scale=0.3]{images/direction-road-maze.jpg}
        \end{itemize}
    \item Means of improvement
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Problem
      \begin{itemize}
        \item MDPs can be computationally intensive
        \item MDPs typically enumerate the entire state and action space
      \end{itemize}
    \item Motivation
      \begin{itemize}
        \item FF-Replan showed MDP determinization and replanning techniques
        \item However, it stops after the first computed path to a goal
        \item May generate same path over and over
        \item Does not generate a policy
      \end{itemize}
    \item Th planning problem
      \begin{itemize}
        \item a domain description
        \item a goal
        \item an initial state
        \item a probability threshold $\rho$
      \end{itemize}
  \end{itemize}

@@

\begin{frame}
  \frametitle{More Questions}

  \begin{itemize}
    \only<1> {\item \textbf{Q}: When aggregating RFF does not update the current partial
      policy. How does this algorithm handles in dynamic environments, whereas
      the current partial policy might be no longer valid?
      \\ \textbf{A}: RFF assumes a MDP, where everything is known. RFF generates
      a policy off-line, but if that policy is used in an environment that does
      not equal to the MDP/world it started with it will fail.
    }

    \only<2> {\item \textbf{Q}: RFF receives a tuple MDP planning problem $(M, s0, G,
      \rho)$, where the states are already defined in M, which means that the
      environment is known.  Is RFF applicable in unknown environments?  If not,
      is it possible to adjust it so that it becomes applicable?
      \\ \textbf{A}: RFF works only for MDPs. In an MDP it is assumed that it is
      fully observable. In cases you describe, it is not, which people invented
      POMDPs for. POMDPs have different algorithms, for example in the paper
      about POMDPs which translates a POMDP to a classical planning problem.
    }
  \end{itemize}
